Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-02-13 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

Although the original validation study suggested a two-factor structure for the IAS, the authors underline its acceptable but imperfect fit [@murphy2019, p. 127], calling on further investigation of the scale's factor structure.
Notably, the authors did not define these factors, as no clear explanations were evident.
They suggested that the first factor reflects the perception of interoceptive signals, while the second pertains to signals that may be difficult to perceive solely through interoceptive information.

>>>>

Although the original validation study suggested a two-factor structure for the IAS, reflecting the perception of [**general?**] interoceptive signals, and that of signals that may be difficult to perceive solely through interoceptive information. However, the authors underline its acceptable but imperfect fit [@murphy2019, p. 127], calling on further investigation of the scale's factor structure.
